---
title: "OKC Thunder Data Science Internship"
author: "Akshay Kirit Kalavadia"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(tidyverse)
library(dplyr)
library(DT)
library(rio)
```
<BR>
<BR>
<BR>
<B>
<FONT SIZE=4, COLOR = "#A11515">
INTRODUCTION AND DATA EXPLORATION
</FONT>
</B>
<P>
<BR>
<FONT SIZE=4> <B>eFG: Effective Fiel Goal</B></FONT>
<P>
<B>Definition:</B> A field goal percentage that is adjusted for made 3 pointers being 1.5 times more valuable than a 2 point shot<BR>
<B>Formula:</B> ((FGM + (0.5 * 3PM))/FGA
```{r}
shots_data <- read.csv("shots_data.csv")
head(shots_data)
summary(shots_data)
str(shots_data)
```
<P>
<P>
Since we want to analyse data of Team-A and Team-B individually, I have created new data frame with individual data of both teams.

<BR>
<FONT SIZE=4, COLOR = "darkblue">
<B>Team-A</B></FONT><BR>
<P>
```{r}
Team_A_shots <- shots_data %>% filter(team == "Team A")
head(Team_A_shots)
```
<P>
<BR>
<FONT SIZE=4, COLOR = "darkblue">
<B>Team-B</B></FONT><BR>
<P>
```{r}
Team_B_shots <- shots_data %>% filter(team == "Team B")
head(Team_B_shots)
```
<BR>
<B>
<FONT SIZE=4, COLOR = "#A11515">
ANALYSIS
</FONT></B>
<BR>
<BR>
<FONT SIZE=4, COLOR = "darkgreen">
<B>Team-A Shot Analysis</B></FONT><BR>
<P>
<BR>
<B> 2 Point Zone </B>

```{r}
shots_2P_Team_A <- Team_A_shots %>%filter((x <= 22 & y<= 7.8)  & (x >= -22 & y <= 7.8) | ((x <= 23.75 & y > 7.8) & (x>= -23.75 & y > 7.8)))
Total_2P_Team_A_attempts <- nrow(shots_2P_Team_A)
Total_2P_Team_A_attempts
```
```{r}
shots_2P_Team_A_percentage = Total_2P_Team_A_attempts/nrow(Team_A_shots) * 100
shots_2P_Team_A_percentage
```
```{r}
Shots_2P_Team_A_converted<-sum(shots_2P_Team_A$fgmade)
Shots_2P_Team_A_converted
```

```{r}
shots_2P_Team_A_eFG = Shots_2P_Team_A_converted / Total_2P_Team_A_attempts * 100
shots_2P_Team_A_eFG
```
<P>
<BR>
<B> Non Corner 3 </B>
```{r}
shots_NC3_Team_A <- Team_A_shots %>%filter((x >= 23.75 & y > 7.8) | (x<= -23.75 & y > 7.8))
Total_NC3_Team_A_attempts <- nrow(shots_NC3_Team_A)
Total_NC3_Team_A_attempts
```
```{r}
shots_NC3_Team_A_percentage = Total_NC3_Team_A_attempts/nrow(Team_A_shots) * 100
shots_NC3_Team_A_percentage
```
```{r}
Shots_NC3_Team_A_converted<-sum(shots_NC3_Team_A$fgmade)
Shots_NC3_Team_A_converted
```

```{r}
shots_NC3_Team_A_eFG = 0
shots_NC3_Team_A_eFG
```
<P>
<BR>
<B> Corner 3 </B>
```{r}
shots_C3_Team_A <- Team_A_shots %>%filter((x >= 22 & y <= 7.8) | (x <= -22 & y <= 7.8))
Total_C3_Team_A_attempts <- nrow(shots_C3_Team_A)
Total_C3_Team_A_attempts
```
```{r}
shots_C3_Team_A_percentage = Total_C3_Team_A_attempts/nrow(Team_A_shots) * 100
shots_C3_Team_A_percentage
```
```{r}
Shots_C3_Team_A_converted<-sum(shots_C3_Team_A$fgmade)
Shots_C3_Team_A_converted
```
```{r}
shots_C3_Team_A_eFG = (Shots_C3_Team_A_converted + (0.5 * Shots_C3_Team_A_converted)) / Total_C3_Team_A_attempts * 100
shots_C3_Team_A_eFG
```
<BR>
<BR>
<FONT SIZE=4, COLOR = "darkgreen">
<B>Team-B Shot Analysis</B></FONT><BR>
<P>
<BR>
<B> 2 Point Zone </B>

```{r}
shots_2P_Team_B <- Team_B_shots %>%filter((x <= 22 & y<= 7.8)  & (x >= -22 & y <= 7.8) | ((x <= 23.75 & y > 7.8) & (x>= -23.75 & y > 7.8)))
Total_2P_Team_B_attempts <- nrow(shots_2P_Team_B)
Total_2P_Team_B_attempts
```

```{r}
shots_2P_Team_B_percentage = Total_2P_Team_B_attempts/nrow(Team_B_shots) * 100
shots_2P_Team_B_percentage
```
```{r}
Shots_2P_Team_B_converted<-sum(shots_2P_Team_B$fgmade)
Shots_2P_Team_B_converted
```

```{r}
shots_2P_Team_B_eFG = Shots_2P_Team_B_converted / Total_2P_Team_B_attempts * 100
shots_2P_Team_B_eFG
```
<P>
<BR>
<B> Non Corner 3 </B>
```{r}
shots_NC3_Team_B <- Team_B_shots %>%filter((x >= 23.75 & y > 7.8) | (x<= -23.75 & y > 7.8))
Total_NC3_Team_B_attempts <- nrow(shots_NC3_Team_B)
Total_NC3_Team_B_attempts
```
```{r}
shots_NC3_Team_B_percentage = Total_NC3_Team_B_attempts/nrow(Team_B_shots) * 100
shots_NC3_Team_B_percentage
```
```{r}
Shots_NC3_Team_B_converted<-sum(shots_NC3_Team_B$fgmade)
Shots_NC3_Team_B_converted
```

```{r}
shots_NC3_Team_B_eFG = 0
shots_NC3_Team_B_eFG
```
<P>
<BR>
<B> Corner 3 </B>
```{r}
shots_C3_Team_B <- Team_B_shots %>%filter((x >= 22 & y <= 7.8) | (x <= -22 & y <= 7.8))
Total_C3_Team_B_attempts <- nrow(shots_C3_Team_B)
Total_C3_Team_B_attempts
```
```{r}
shots_C3_Team_B_percentage = Total_C3_Team_B_attempts/nrow(Team_B_shots) * 100
shots_C3_Team_B_percentage
```
```{r}
Shots_C3_Team_B_converted<-sum(shots_C3_Team_B$fgmade)
Shots_C3_Team_B_converted
```
```{r}
shots_C3_Team_B_eFG = (Shots_C3_Team_B_converted + (0.5 * Shots_C3_Team_B_converted)) / Total_C3_Team_B_attempts * 100
shots_C3_Team_B_eFG

((5 + (0.5*5)) / Total_C3_Team_B_attempts) * 100 
```

```{r}
Summary_Team_A <- data.frame(
                       Shot_Zone = c("2PT", "NC3", "C3"),
                       Shot_Distribution = c(round(shots_2P_Team_A_percentage,3), round(shots_NC3_Team_A_percentage,3), round(shots_C3_Team_A_percentage,3)),
                      eFG = c(round(shots_2P_Team_A_eFG,3), round(shots_NC3_Team_A_eFG,3), round(shots_C3_Team_A_eFG,3)))
datatable(Summary_Team_A,options = list(paging = F))
```

```{r}
Summary_Team_B <- data.frame(
                       Shot_Zone = c("2PT", "NC3", "C3"),
                       Shot_Distribution = c(round(shots_2P_Team_B_percentage,3), round(shots_NC3_Team_B_percentage,3), round(shots_C3_Team_B_percentage,3)),
                      eFG = c(round(shots_2P_Team_B_eFG,3), round(shots_NC3_Team_B_eFG,3), round(shots_C3_Team_B_eFG,3)))
datatable(Summary_Team_B,options = list(paging = F))
```
